\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2016-05-10 paper/ms.tex
The model specification

\section{Implementing models}

@@

This first chooses a random integer from $[0, 3)$ using the
\code{rand\_int(int)} member function of the \code{DNest4::RNG} class.

>>>>

\section{Implementing models}
The ``classic'' method of implementing models in \pkg{DNest4} is by
writing a \proglang{C++} class, an object of which represents a
point in your parameter space.

To demonstrate, consider a simple linear regression situation where the
sampling distribution is
\begin{align}
y_i | m, b, \sigma &\sim \textnormal{Normal}(mx_i + b, \sigma^2)
\end{align}
and the priors are
\begin{align}
m &\sim \textnormal{Normal}(0, 1000^2)\\
b &\sim \textnormal{Normal}(0, 1000^2)\\
\ln\sigma &\sim \textnormal{Uniform}(-10, 10)
\end{align}
These are naive diffuse priors and we do not claim any special status for them.

@@

This first chooses a random integer from $[0, 3)$ using the
\code{rand\_int(int)} member function of the \code{DNest4::RNG} class.
This determines which of the three parameters is modified.
